\documentclass[11pt]{article}

\usepackage[top=1cm, left=2.25cm, right=2.25cm, bottom=1cm]{geometry}

\usepackage[utf8]{inputenc} 
\usepackage{amsmath}
\usepackage{siunitx} % \num
\usepackage{bm}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{url}
\usepackage{fontawesome}
\usepackage{enumitem}

\pagestyle{empty}

\renewcommand{\arraystretch}{1.4} %more space between table rows

\title{\Huge\textsc{Conor John Williams}}
\date{}

\author{Email: cw$648$@cam.ac.uk \\ Phone: $+44$ $7479$ $476483$ \\ Address: Churchill College, Storey's Way, Cambridge, CB$3$ $0$DS}

\begin{document}

\maketitle

\thispagestyle{empty}

\renewcommand{\arraystretch}{1.5} %more space between table rows

\section*{Education} \label{sec:intro}

\begin{tabular}{@{}lp{0.84\textwidth}@{}}
    \textbf{2020--today}: & \textbf{PhD Computational Methods, University of Cambridge.}

    \vspace{0.5em}
    
    Supervised by Professor James Elliott – due for submission in summer 2024.
    
    \vspace{0.5em}
    
    Industrial collaboration with \textbf{sponsor, Rolls-Royce} - understanding the atomistic mechanisms of hydrogen-embrittlement.  
    
    \vspace{0.5em}
    
    My specialisations are: molecular modelling, numerical methods, massively parallel processing, GPGPU computing and invariant representation theory.
    
    \vspace{0.5em}
    
    Reviewed after first-year probationary period as ``\textbf{a very impressive candidate} [who] is well placed to make an impact in the field''.      \\
    
    \textbf{2019--2020}:  & \textbf{MPhil, Distinction (\num{83}\% average)}, Scientific Computing, University of Cambridge.
    
    \vspace{0.5em}
    
    Courses in distributed computing, parallel programming, GPU programming and stochastic/dynamic modelling.
    
    \vspace{0.5em}
    
    \textbf{Distinction-awarded dissertation} titled: Off-lattice kinetic Monte Carlo modelling and numerical methods.                                  \\
    
    \textbf{2016--2019}:  & \textbf{BA (Hons), 1\textsuperscript{st} class (in all years)}, Natural Sciences Tripos (Physics), University of Cambridge. \\
    
    \textbf{2014--2016}:  & \textbf{A-levels, straight A* grades}, in Mathematics, Physics, Chemistry and Biology, Colchester Royal Grammar School.     \\
    
    \textbf{2009--2014}:  & \textbf{GCSEs, 8 A* grades}, Tendring Technology College.
    
\end{tabular}

\section*{Industry}

\paragraph*{Summer 2023} Machine learning intern at \textbf{Myrtle.ai}. I developed a custom LSTM module in CUDA to replace a pytorch implementation. This formed a key component of their FPGA automatic speech recognition pipeline. I \textbf{delivered a solution that was $7.7\times$ faster} than their previous implementation and throughput competitive with NVIDIA's hand-tuned CuDNN library. Furthermore, during my time there I identified several stages in the memory constraining section of the model training pipeline that could be optimized; ultimately I increased the training batch size by $85\%$ which reduced training times/costs by a similar fraction. Finally, I implemented the transducer Multi-blank extension and trained a model with competitive word-error-rates whilst \textbf{halving inference-time latency}. 

\section*{Publications}

C.J. Williams, E.I. Galindo-Nava, Accelerating off-lattice kinetic Monte Carlo
simulations to predict hydrogen vacancy-cluster interactions in $\alpha$-Fe, Acta Mater.\ (2022), doi:
\href{https://doi.org/10.1016/j.actamat.2022.118452}{10.1016/j.actamat.2022.118452}

\section*{Conferences}

\textbf{TMS2023} \emph{Symposium of Computational Thermodynamics and Kinetics}, presented on advanced materials simulation at one of the largest and most prestigious materials-science conferences worldwide.

% \pagebreak


\section*{Other employment}

\paragraph*{2022--2023} \textbf{Masters dissertation supervisor}. In this role I guided a student on their first novel-research: \emph{modelling vacancy-cluster stability}. This involved bi-weekly meetings, reviewing their work and steering them towards a publication-quality dissertation. They achieved the \textbf{highest-grade in their cohort} and won the departmental prize for this work.

\paragraph*{2020--2023}

I have taught for three year as an \textbf{undergraduate mathematics supervisor} at the University of Cambridge. This requires me to set, mark and teach eight students every week. This year one of my students ranked $2\textsuperscript{nd}$ across all the Cambridge colleges. Feedback has included: ``[Conor] pushed me to see the deep-connections between the topics we studied and always had the most (frustratingly!) elegant solutions''. 

\paragraph*{2020-2021} While holding a senior role on the Churchill College MCR as the Bar Secretary I: transformed the bar's stock list; negotiated extended opening hours and recruited and trained one of the largest cohorts of staff in recent years. I was required to plan-ahead, work diplomatically and assertively with the MCR team and communicating with Senior College leadership.

\section*{Software projects - available on \href{https://github.com/ConorWilliams}{ GitHub \faGithub}}

\paragraph*{2022--today} I am currently undertaking the open-sourcing and documentation of my PhD codebase, the first open off-lattice kinetic Monte Carlo framework. 

\paragraph*{2021--today} Developed and maintain C++ implementations of concurrent data-structures and a lock-free \textbf{continuation-stealing scheduler} (utilizing C++20's coroutines) as part of my journey to understand parallel/asynchronous programming and memory models.

\paragraph*{2021} As the MCR Computing Officer I designed and maintained a digital room-ballot system for the College, attempting to solve \emph{the assignment problem}.

\paragraph*{2018} Developed an optimisation algorithm in Python for eWATERservices to position water taps in African villages, which formed part of their successful World Bank investment bid. 

\section*{Technical skills}
\begin{itemize}[leftmargin=*]
    \setlength{\itemsep}{0pt}
    \item \textbf{Coding:} C++ (expert/advanced); CUDA, Python \&  Git (intermediate); MATLAB$\text{\textregistered}$ (basic).
    \item \textbf{Operating systems:} Linux, Windows.
    \item \textbf{Software/Libraries:} \LaTeX, Pytorch, Eigen, Sphinx, Doxygen, Microsoft Office.
    \item \textbf{Presentations:} I regularly give engaging and informative talks to my non-expert industrial sponsors. Alongside, \textbf{clear and precise technical-presentations} to my research group and department.
          
\end{itemize}

\pagebreak

\section*{Interests}

\begin{itemize}[leftmargin=*]
    \setlength{\itemsep}{0pt}
    \item I am an avid ultralight-backpacker - completing multiple $40+$ day expeditions, carrying the minimum amount of equipment. These require extended planning and high self-motivation.
          
    \item I have rowed competitively for my college for four years, training as much as five times a week. This demonstrates my commitment and time management.
          
    \item I am an accomplished dinghy sailor; qualified Day Skipper; active member of the CUYC yacht club; amateur runner and surfer. These hobbies have taught me to work as a team in high-pressured environments.
\end{itemize}


% \section*{References}

% \centering

% Available on request.

\end{document}